---
title: "PhysMove: Space-Use Patterns"
author: "Hannah Calich, Jorge Rodríguez, Víctor Eguíluz & Ana Sequeira"
date: "Last updated: `r Sys.Date()`"
output:
  officedown::rdocx_document:
    reference_docx: "template.docx"
    plots:
      style: Figure
      align: center
    tables:
      style: Table
tables: yes
vignette: |
  %\VignetteEncoding{UTF-8}  
  %\VignetteIndexEntry{PhysMove: Introduction}  
  %\VignetteEngine{knitr::rmarkdown}
---

<style>
      img {
      border: 0;
    }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(#dpi = 600, 
                      fig.align = 'center', 
                      #fig.width = 4, 
                      #fig.height = 3,
                      echo = TRUE,
                      collapse = TRUE,
                      fig.path = "images/",
                      comment = "#>") 
```

setwd("~/2024/PhysMove/PhysMove_Git/PhysMove")

```{r load physmove space-use vignette, echo=FALSE}
# Load PhysMove
library(PhysMove)
```

<br>  
```{r occ_map, echo=TRUE, message=FALSE, fig.width=5, fig.height=3.5}
# Create an occupancy map based on the tracks dataset
Occ <- occupancy(tracks)
```

<br>  
```{r summarise occ, echo=TRUE}
# Summarize occupancy results
summary(Occ) 
```

**Figure** **V13** Map of occupancy patterns from the `tracks` dataset. Map created with `Occupancy()` default parameters.

<br>
```{r summary occ, echo=FALSE, warning=FALSE, message=FALSE} 
library(kableExtra)

table <- as.data.frame.matrix(summary(Occ))
row.names(table) <- NULL

table %>%
    kable("html", align="l") %>%
    kableExtra::kable_styling(bootstrap_options = c("condensed"), full_width = F, html_font = "Consolas", font_size = 35) %>%
    kableExtra::column_spec(1:4, width_min = "400px") %>%
    kableExtra::column_spec(5, width_min = "585px") %>%
    kableExtra::row_spec(0:nrow(table), background = "#F8F8F8", color = "#60a0b0", extra_css = "padding-top: 0px !important; padding-bottom: 0px !important") %>%
    kableExtra::save_kable("vignettes/word_formatted/tables/summary_occ.png", zoom=1) # html files cant be output to word
```

```{r occ_pdf, echo=TRUE}
# Create a pdf plot of occupancy values
pdf.occ  <- plotPDF(Occ$Occupancy, desc="occupancy")
```

**Figure V14** Probability density function (pdf) plot of occupancy values for the tracks dataset calculated with `Occupancy()` default parameters. Plot created using `PlotPDF()` with `desc=“Occupancy”`.

```{r load infomap, eval=TRUE, message=FALSE, warning=FALSE}
# Identify community-wide movements 
setwd("~/2024/PhysMove") # Update your working directory to the folder containing the infomap file
library(infomapecology) 
infomapResult <- infomapCommunities(tracks)
setwd("~/2024/PhysMove/PhysMove_Git/PhysMove")
```

```{r run infomap on sample, echo=TRUE, message=FALSE, warning=FALSE}
# View the Infomap monolayer object structure
str(infomapResult[["infomap_object"]])
```

```{r str infomap, echo=FALSE, warning=FALSE, message=FALSE} 
library(kableExtra)

table <- as.data.frame(capture.output(str(infomapResult[["infomap_object"]])))
names(table) <- NULL
# table <- table[-1,]
row.names(table) <- NULL

table %>%
    kable("html", align="l") %>%
    kableExtra::kable_styling(bootstrap_options = c("condensed"), full_width = F, html_font = "Consolas", font_size = 35) %>%
    kableExtra::column_spec(1, width_min = "2185px") %>%  
    kableExtra::row_spec(1:nrow(table), background = "#F8F8F8", color = "#60a0b0", extra_css = "padding-top: 0px !important; padding-bottom: 0px !important") %>%
    kableExtra::save_kable("vignettes/word_formatted/tables/infomap_str.png", zoom=1) # html files cant be output to word
```

```{r infomap_map, echo=TRUE, message=FALSE, fig.width=5, fig.height=3.5}
# Create a map of the Infomap communities
communityMap(infomapResult)
```

**Figure** **v15** Map illustrating level 1 Infomap communities from the `tracks` dataset determined using `InfomapCommunities()` default parameters. Map created with `CommunityMap()` default parameters.
